Non-word repetition in Yélî Dnye

### 2021-01-21 manuscript.Rmd
minor

1. add a table with sample studies & languages & their characteristiscs
1. be accurate on what hasn't been done x-ling speaking
1. try to find data on length distribution across languages to see if this fits length differences
1. to the above, add sylable characteristics, inventory size, inventory compactness
1. fix camila ref

@@

>>>>

1. add SDs to https://docs.google.com/spreadsheets/d/1f4X7SmP4flhPlCEtvyqp_ERgMp5SC8qHCaMHj93C_FU/edit#gid=44537533
1. add a table with sample studies & languages & their characteristiscs
1. be accurate on what hasn't been done x-ling speaking
1. try to find data on length distribution across languages to see if this fits length differences
1. to the above, add sylable characteristics, inventory size, inventory compactness
1. revise intro
1. revise discussion

@@

- despite 4-syll being rare, they are repeated correctly
- similar levels of IDS in Tsi & YD, yet very different results: overall NWR, effect of length
- conclusions Cristia about long-term effects perhaps don't hold
- or perhaps input estimation is inaccurate -- talk about different ways of estimating input quantity across papers and uncertainty in estimates
- or perhaps it's about the prevalence of literacy in the population -- phonetic effects of learning to read & consequences in young children's encoding and decoding of sounds for NWR
- differences in test: group versus individual, level of training of RA, from the same community or not, model was native or not, heard over headphones or not
